### 2022-02-13 prior_versions/arxiv/proof_gaussian_case.tex
update

\section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
%We first state the asymptotic limit for the bias equation \eqref{eq_bias_2task}.

%\begin{theorem}\label{thm_main_RMT_app}
%
%	In the setting of Theorem \ref{thm_main_RMT},
%\end{theorem}
%For the rest of this section, we present the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}

%\paragraph{Proof Overview (cont'd).}
%We continue the proof overview of Theorem \ref{thm_main_RMT} and \ref{thm_main_RMT_app} from Section \ref{sec_diff}.
%Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.
%Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$.

We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
By the rotational invariance of the multivariate Gaussian distribution, we have that the entries of $Z^{(1)} U$ and $Z^{(2)}V$ also follow an isotropic Gaussian distribution.
Hence it suffices to consider the following resolvent
 \begin{equation} \label{resolv Gauss1}
   G(z)= \left( {\begin{array}{*{20}c}
   { -z\id_{p\times p} } & (n_1+n_2)^{-1/2}\Lambda (Z^{(1)})^\top & (n_1+n_2)^{-1/2} (Z^{(2)})^\top  \\
   {(n_1+n_2)^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
   {(n_1+n_2)^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
   \end{array}} \right)^{-1}.
 \end{equation}
We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a}.
We first introduce several useful notations. We define $n:=n_1+n_2$ and the following index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
%We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$.
%Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
%	\be\label{labelZ}
% Z^{(1)}= [Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1], \quad Z^{(2)}= [Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2].\ee
We will study the following partial traces of the resolve $G(z)$:
\be\label{defm}
\begin{split}
m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
 m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z).
\end{split}
\ee
To deal with the matrix inverse, we consider the following resolvent minors of $G(z)$.
\begin{definition}[Resolvent minors]\label{defn_Minor}
	Let $X \in \real^{(p + n_1 + n_2)\times (p + n_1 + n_2)}$ and $i = 1, 2, \dots, p + n_1 + n_2$.
	The minor of $X$ after removing the $i$-th row and column of $X$ is denoted by $X^{(i)} := [X_{a_1a_2}:a_1, a_2 \in \mathcal I\setminus \{i\}]$ as a square matrix with dimension $p + n_1 + n_2 - 1$.
	For the indices of $X^{(i)}$, we use $X^{(i)}_{a_1 a_2}$ to denote $ X_{a_1 a_2}$ when $a_1$ and $a_2$ are both not equal to $i$, and $X^{(i)}_{a_1 a_2}=0$ when $a_1 = i$ or $a_2 = i$.
	The resolvent minor of $G(z)$ after removing the $i$-th row and column is defined as
	\begin{align*}
		G^{(i)}(z) := \left[ \left( {\begin{array}{*{20}c}
		  { -z\id_{p\times p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
      {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
			{n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
    \end{array}} \right)^{(i)}\right]^{-1}.
	\end{align*}
\end{definition}
As a remark, we define the partial traces $m^{(i)}(z)$, $m_0^{(i)}(z)$, $m_1^{(i)}(z)$, and $m_2^{(i)}(z)$ by replacing $G(z)$ with $G^{(i)}(z)$ in equation \eqref{defm}.

@@

%\be\label{approx m12 add}
%(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
%\ee

Next, we apply standard concentration bounds to simplify the above results.
For $G^{-1}_{i i}(z)$, recall that the resolvent minor $G^{(i)}$ is defined such that it is independent of the $i$-th row and column of $Z^{(1)}$ and $Z^{(2)}$.
Hence by standard concentration inequalities, we have that the cross terms are approximately zero.
%is approximately equal to the expectation over $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$.
As shown in Lemma \ref{lemm_selfcons_weak}, we have that with high probability the following holds
\begin{align*}
	G_{ii}^{-1}(z) &= -z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1) \\
	&= - z - \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1^{(i)}(z)-  \frac{n_2}{n_1 + n_2} m_2^{(i)}(z)+\oo(1),
\end{align*}
by our definition of the partial traces $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$. %with respect to the resolvent minor $G^{(i)}(z)$.
Since we have removed only one column and one row from $H(z)$, $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ should be approximately equal to $m_1(z)$ and $m_2(z)$.
Hence we obtain that
\begin{align}\label{1self_Gii}
	G_{ii}(z)  = -\left(z + \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1(z) +  \frac{n_2}{n_1 + n_2} m_2(z) + \oo(1)\right)^{-1}.
\end{align}
For the other two blocks $\cal I_1$ and $\cal I_2$, using similar ideas we obtain the following equations with high probability:
\begin{align*}
	G_{\mu\mu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1},\\ 
	G_{\nu\nu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
\end{align*}
By averaging the above results over $\mu \in \cal I_1$ and $\nu \in \cal I_2$, we obtain that with high probability
\begin{align*}
	m_1(z) &= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) = -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} ,\\
	m_2(z) &= \frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}(z) = -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
\end{align*}
Furthermore, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability
$G_{\mu\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu\nu}(z) = m_2+\oo(1)$.
In other words, both block matrices within $\cal I_1$ and $\cal I_2$ are approximately a scaling of the identity matrix.
The above results for $m_1(z)$ and $m_2(z)$ imply that
\begin{align*}
	m_1^{-1}(z) &= -1- \frac{1}{n } \sum_{i=1}^p \lambda_i^2 G_{ii}(z)+ \oo(1),\\ 
	 m_2^{-1}(z) &= -1- \frac{1}{n } \sum_{i=1}^p G_{ii}(z)  + \oo(1),
\end{align*}
where we used the definitions of $m(z)$ and $m_0(z)$.
By applying equation \eqref{1self_Gii} for $G_{i i}(z)$ to these two equations, we obtain the system of self-consistent equations \eqref{approximate m1m2}.
In Lemma \ref{lem_stabw}, we show that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.

\paragraph{Matrix limit.}
Finally, we derive the matrix limit $\Gi(z)$.
We have shown that $m_1(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_1} a_1(z) $ and $m_2(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_2(z)$ because we know that \eqref{approximate m1m2} holds.
Inserting $m_1(z)$ and $m_2(z)$ into equation \eqref{1self_Gii}, we get that for $i$ in $\cal I_0$,
$G_{ii}(z) = (-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1))^{-1}$ with high probability.
For $\mu$ in $\cal I_1$ and $\nu$ in $\cal I_2$, by $G_{\mu\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu\nu}(z) = m_2+\oo(1)$, we have that $G_{\mu \mu}(z) = -\frac{n_1 + n_2}{n_1}a_{1}(z)+\oo(1)$ and $G_{\nu\nu}(z) = -\frac{n_1 + n_2}{n_2}a_{2}(z)+\oo(1)$ with high probability.
Hence we have derived the diagonal entries of $\Gi(z)$.
In Lemma \ref{Z_lemma}, we show that the off-diagonal entries are close to zero.
For example, for $i\ne j\in \cal I_0$, by Schur complement, we have that
$$G_{ij}(z) = -G_{ii}(z)\cdot {n^{-1/2}}\Big({\lambda_i}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}(z) + \sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}(z) \Big).$$
Using standard concentration inequalities, we can show that $\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}(z)$ and $\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}(z)$ are both close to zero.
The other off-diagonal entries are bounded similarly.
%The bound on the off-diagonal entries will be proved rigorously .

@@

\begin{definition}[Stochastic domination]\label{stoch_domination}
Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
%\HZ{what is $n$-dependent rv?}[{\cor Most variables in our paper are $n$-dependent implicitly, such as resolvents. Furthermore, the random matrix entries can also depend on $n$ if we want. One important example is Bernoulli random variable with sparsity $p=n^{-\theta}$. Furthermore, this also includes the random variables that do not depend on $n$ as a special case.}]
We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for all $n > n_0(\e, D)$,
\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}. \]
In case $\xi(u)$ and $\zeta(u)$ is a function of $u$ supported in $\cal U$, then we say $\xi(u)$ is stochastically dominated by $\zeta(u)$ uniformly in $\cal U$ if % for any constants $\e, D>0$,
\[ \sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}. \]
\end{definition}

%For example, we say that $\xi$ is stochastically dominated by $\zeta$ with overwhelming probability if $\zeta$ is greater than $\xi$ up to a small power of $n^{\e}$.
We make several remarks.
First, since we allow an $n^\e$ factor in stochastic domination, we can ignore $\log$ factors without loss of generality since $(\log n)^C\prec 1$ for any constant $C>0$.
Second, given a random variable $\xi$ whose moments exist up to any order, we have that $|\xi|\prec 1$.
This is because by Markov's inequality, let $k$ be larger than $D/ \e$, then we have that
$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D}.$$
As a special case, this implies that a Gaussian random variable $\xi$ with unit variance satisfies that $|\xi|\prec 1$.

@@

%In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below. %\ref{sec_prelim}.
%Then Theorem \ref{thm_main_RMT} will follow from this result as immediate corollaries. We first state the exact assumptions needed for our purpose.

Next, we introduce the bounded support assumption for a random matrix.
We say that a random matrix $Z \in\real^{n \times p}$ satisfies the {\it{bounded support condition}} with $Q$ or $Z$ has support $Q$ if
\begin{equation}
	\max_{1\le i \le n, 1 \le j \le p}\vert Z_{i j} \vert \prec Q. \label{eq_support}
\end{equation}
As shown in the example above, if the entries of $Z$ have finite moments up to any order, then $Z$ has bounded support $1$.
More generally, if the entries of $Z$ have finite $\varphi$-th moment, then using Markov's inequality and a simple union bound we get that %\HZ{I don't fully get the equation below}
\begin{align}
	\P\left(\max_{1\le i\le n, 1\le j \le p}|Z_{i  j}|\ge (\log n) n^{\frac{2}{\varphi}}\right) &\le \sum_{i=1}^n \sum_{j=1}^p \P\left(|Z_{i j}|\ge (\log n) n^{\frac{2}{\varphi}}\right)  \nonumber\\
	&\le \sum_{i=1}^n \sum_{j=1}^p \frac{C(\varphi)}{\left[(\log n) n^{\frac{2}{\varphi}}\right]^\varphi} = \OO((\log n)^{-\varphi}).\label{Ptrunc}
	\end{align}
In other words, $Z$ has bounded support $Q=n^{\frac{2}{\varphi}}$ with high probability.

The following resolvent identities are important tools for our proof. Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}, and matrix $\AF$ is given in equation \eqref{defn AF}. %\eqref{diagW}.
\begin{lemma}\label{lemm_resolvent}
We have the following resolvent identities.
\begin{itemize}
	\item[(i)] For $i\in \mathcal I_1$ and $\mu\in \mathcal I_1\cup \cal I_2$, we have
		\begin{equation}
			\frac{1}{G_{ii}} =  - z - \left( {\AF G^{\left( i \right)} \AF^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {\AF^\top  G^{\left( \mu  \right)} \AF} \right)_{\mu \mu }.\label{resolvent2}
		\end{equation}
	\item[(ii)] For $i\in \mathcal I_1$, $\mu \in \mathcal I_1\cup \cal I_2$, $a\in \cal I\setminus \{i\}$ and $b\in \cal I\setminus \{ \mu\}$, we have
		\begin{equation}
			G_{ia}   = -G_{ii}  \left( \AF G^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( \AF^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
		\end{equation}
%For $i\in \mathcal I_1$ and $\mu\in \mathcal I_2$, we have
%\begin{equation}\label{resolvent6}
%\begin{split}
% G_{i\mu } =  -G_{ii}  \left( WG^{\left( {i} \right)} \right)_{i\mu}, \quad G_{\mu i}= -G_{\mu\mu}\left( W^\top G^{(\mu)}\right)_{\mu i}. %\left( { - Y_{i\mu }  +  {\left( {YG^{\left( {i\mu } \right)} Y} \right)_{i\mu } } } \right) . %, \ \  G_{\mu i}  = G_{\mu \mu } G_{ii}^{\left( \mu  \right)} \left( { - Y_{\mu i}^\top  + \left( {Y^\top  G^{\left( {\mu i} \right)} Y^\top  } \right)_{\mu i} } \right).
%\end{split}
%\end{equation}
 \item[(iii)] For $a \in \mathcal I$ and $a_1,a_2 \in \mathcal I \setminus \{a\}$, we have
		\begin{equation}
			G_{a_1a_2}^{\left( a \right)}  = G_{a_1a_2}  - \frac{G_{a_1a} G_{aa_2}}{G_{aa}}.
%, \quad  \frac{1}{{G_{{b}{b}} }} = \frac{1}{{G_{{b}{b}}^{({a})} }} - \frac{{G_{{b}{a}} G_{{a}{b}} }}{{G_{{b}{b}} G_{{b}{b}}^{({a})} G_{{a}{a}} }}.
			\label{resolvent8}
		\end{equation}
%and
%\begin{equation}
%\frac{1}{{G_{ss} }} = \frac{1}{{G_{ss}^{(r)} }} - \frac{{G_{sr} G_{rs} }}{{G_{ss} G_{ss}^{(r)} G_{rr} }}.
%\label{resolvent9}
%\end{equation}
% \item[(iv)]
%All of the above identities hold for $G^{(\mathbb T)}$ instead of $G$ for $\mathbb T \subset \mathcal I$, and in the case where $A$ and $B$ are not diagonal.
\end{itemize}
\end{lemma}
The above result can be proved using Schur's complement formula, cf. \citet[Lemma 4.4]{Anisotropic}.

>>>>

\section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}

We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
By the rotational invariance of the multivariate Gaussian distribution, we have that the entries of $Z^{(1)} U$ and $Z^{(2)}V$ also follow an isotropic Gaussian distribution.
Hence it suffices to consider the following resolvent
 \begin{equation} \label{resolv Gauss1}
   G(z)= \left( {\begin{array}{*{20}c}
   { -z\id_{p\times p} } & (n_1+n_2)^{-1/2}\Lambda (Z^{(1)})^\top & (n_1+n_2)^{-1/2} (Z^{(2)})^\top  \\
   {(n_1+n_2)^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
   {(n_1+n_2)^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
   \end{array}} \right)^{-1}.
 \end{equation}
We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a}.
We first introduce several useful notations. We define $n:=n_1+n_2$ and the following index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
We will study the following partial traces of the resolve $G(z)$:
\be\label{defm}
\begin{split}
m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
 m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z).
\end{split}
\ee
To deal with the matrix inverse, we consider the following resolvent minors of $G(z)$.
\begin{definition}[Resolvent minors]\label{defn_Minor}
	Let $X \in \real^{(p + n_1 + n_2)\times (p + n_1 + n_2)}$ and $i = 1, 2, \dots, p + n_1 + n_2$.
	The minor of $X$ after removing the $i$-th row and column of $X$ is denoted by $X^{(i)} := [X_{a_1a_2}:a_1, a_2 \in \mathcal I\setminus \{i\}]$ as a square matrix with dimension $p + n_1 + n_2 - 1$.
	For the indices of $X^{(i)}$, we use $X^{(i)}_{a_1 a_2}$ to denote $ X_{a_1 a_2}$ when $a_1$ and $a_2$ are both not equal to $i$, and $X^{(i)}_{a_1 a_2}=0$ when $a_1 = i$ or $a_2 = i$.
	The resolvent minor of $G(z)$ after removing the $i$-th row and column is defined as
	\begin{align*}
		G^{(i)}(z) := \left[ \left( {\begin{array}{*{20}c}
		  { -z\id_{p\times p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
      {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
			{n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
    \end{array}} \right)^{(i)}\right]^{-1}.
	\end{align*}
\end{definition}
As a remark, we define the partial traces $m^{(i)}(z)$, $m_0^{(i)}(z)$, $m_1^{(i)}(z)$, and $m_2^{(i)}(z)$ by replacing $G(z)$ with $G^{(i)}(z)$ in equation \eqref{defm}.

@@

Next, we apply standard concentration bounds to simplify the above results.
For $G^{-1}_{i i}(z)$, recall that the resolvent minor $G^{(i)}$ is defined such that it is independent of the $i$-th row and column of $Z^{(1)}$ and $Z^{(2)}$.
Hence by standard concentration inequalities, we have that the cross terms are approximately zero.
As shown in Lemma \ref{lemm_selfcons_weak}, we have that with high probability the following holds
\begin{align*}
	G_{ii}^{-1}(z) &= -z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1) \\
	&= - z - \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1^{(i)}(z)-  \frac{n_2}{n_1 + n_2} m_2^{(i)}(z)+\oo(1),
\end{align*}
by our definition of the partial traces $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$. %
Since we have removed only one column and one row from $H(z)$, $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ should be approximately equal to $m_1(z)$ and $m_2(z)$.
Hence we obtain that
\begin{align}\label{1self_Gii}
	G_{ii}(z)  = -\left(z + \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1(z) +  \frac{n_2}{n_1 + n_2} m_2(z) + \oo(1)\right)^{-1}.
\end{align}
For the other two blocks $\cal I_1$ and $\cal I_2$, using similar ideas we obtain the following equations with high probability:
\begin{align*}
	G_{\mu\mu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1},\\ 
	G_{\nu\nu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
\end{align*}
By averaging the above results over $\mu \in \cal I_1$ and $\nu \in \cal I_2$, we obtain that with high probability
\begin{align*}
	m_1(z) &= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) = -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} ,\\
	m_2(z) &= \frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}(z) = -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
\end{align*}
Furthermore, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability
$G_{\mu\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu\nu}(z) = m_2+\oo(1)$.
In other words, both block matrices within $\cal I_1$ and $\cal I_2$ are approximately a scaling of the identity matrix.
The above results for $m_1(z)$ and $m_2(z)$ imply that
\begin{align*}
	m_1^{-1}(z) &= -1- \frac{1}{n } \sum_{i=1}^p \lambda_i^2 G_{ii}(z)+ \oo(1),\\ 
	 m_2^{-1}(z) &= -1- \frac{1}{n } \sum_{i=1}^p G_{ii}(z)  + \oo(1),
\end{align*}
where we used the definitions of $m(z)$ and $m_0(z)$.
By applying equation \eqref{1self_Gii} for $G_{i i}(z)$ to these two equations, we obtain the system of self-consistent equations \eqref{approximate m1m2}.
In Lemma \ref{lem_stabw}, we show that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.

\paragraph{Matrix limit.}
Finally, we derive the matrix limit $\Gi(z)$.
We have shown that $m_1(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_1} a_1(z) $ and $m_2(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_2(z)$ because we know that \eqref{approximate m1m2} holds.
Inserting $m_1(z)$ and $m_2(z)$ into equation \eqref{1self_Gii}, we get that for $i$ in $\cal I_0$,
$G_{ii}(z) = (-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1))^{-1}$ with high probability.
For $\mu$ in $\cal I_1$ and $\nu$ in $\cal I_2$, by $G_{\mu\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu\nu}(z) = m_2+\oo(1)$, we have that $G_{\mu \mu}(z) = -\frac{n_1 + n_2}{n_1}a_{1}(z)+\oo(1)$ and $G_{\nu\nu}(z) = -\frac{n_1 + n_2}{n_2}a_{2}(z)+\oo(1)$ with high probability.
Hence we have derived the diagonal entries of $\Gi(z)$.
In Lemma \ref{Z_lemma}, we show that the off-diagonal entries are close to zero.
For example, for $i\ne j\in \cal I_0$, by Schur complement, we have that
$$G_{ij}(z) = -G_{ii}(z)\cdot {n^{-1/2}}\Big({\lambda_i}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}(z) + \sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}(z) \Big).$$
Using standard concentration inequalities, we can show that $\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}(z)$ and $\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}(z)$ are both close to zero.
The other off-diagonal entries are bounded similarly.

@@

\begin{definition}[Stochastic domination]\label{stoch_domination}
Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for all $n > n_0(\e, D)$,
\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}. \]
In case $\xi(u)$ and $\zeta(u)$ is a function of $u$ supported in $\cal U$, then we say $\xi(u)$ is stochastically dominated by $\zeta(u)$ uniformly in $\cal U$ if %
\[ \sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}. \]
\end{definition}

We make several remarks.
First, since we allow an $n^\e$ factor in stochastic domination, we can ignore $\log$ factors without loss of generality since $(\log n)^C\prec 1$ for any constant $C>0$.
Second, given a random variable $\xi$ whose moments exist up to any order, we have that $|\xi|\prec 1$.
This is because by Markov's inequality, let $k$ be larger than $D/ \e$, then we have that
$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D}.$$
As a special case, this implies that a Gaussian random variable $\xi$ with unit variance satisfies that $|\xi|\prec 1$.

@@

Next, we introduce the bounded support assumption for a random matrix.
We say that a random matrix $Z \in\real^{n \times p}$ satisfies the {\it{bounded support condition}} with $Q$ or $Z$ has support $Q$ if
\begin{equation}
	\max_{1\le i \le n, 1 \le j \le p}\vert Z_{i j} \vert \prec Q. \label{eq_support}
\end{equation}
As shown in the example above, if the entries of $Z$ have finite moments up to any order, then $Z$ has bounded support $1$.
More generally, if the entries of $Z$ have finite $\varphi$-th moment, then using Markov's inequality and a simple union bound we get that %
\begin{align}
	\P\left(\max_{1\le i\le n, 1\le j \le p}|Z_{i  j}|\ge (\log n) n^{\frac{2}{\varphi}}\right) &\le \sum_{i=1}^n \sum_{j=1}^p \P\left(|Z_{i j}|\ge (\log n) n^{\frac{2}{\varphi}}\right)  \nonumber\\
	&\le \sum_{i=1}^n \sum_{j=1}^p \frac{C(\varphi)}{\left[(\log n) n^{\frac{2}{\varphi}}\right]^\varphi} = \OO((\log n)^{-\varphi}).\label{Ptrunc}
	\end{align}
In other words, $Z$ has bounded support $Q=n^{\frac{2}{\varphi}}$ with high probability.

The following resolvent identities are important tools for our proof. Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}, and matrix $\AF$ is given in equation \eqref{defn AF}. %
\begin{lemma}\label{lemm_resolvent}
We have the following resolvent identities.
\begin{itemize}
	\item[(i)] For $i\in \mathcal I_1$ and $\mu\in \mathcal I_1\cup \cal I_2$, we have
		\begin{equation}
			\frac{1}{G_{ii}} =  - z - \left( {\AF G^{\left( i \right)} \AF^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {\AF^\top  G^{\left( \mu  \right)} \AF} \right)_{\mu \mu }.\label{resolvent2}
		\end{equation}
	\item[(ii)] For $i\in \mathcal I_1$, $\mu \in \mathcal I_1\cup \cal I_2$, $a\in \cal I\setminus \{i\}$ and $b\in \cal I\setminus \{ \mu\}$, we have
		\begin{equation}
			G_{ia}   = -G_{ii}  \left( \AF G^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( \AF^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
		\end{equation}
 \item[(iii)] For $a \in \mathcal I$ and $a_1,a_2 \in \mathcal I \setminus \{a\}$, we have
		\begin{equation}
			G_{a_1a_2}^{\left( a \right)}  = G_{a_1a_2}  - \frac{G_{a_1a} G_{aa_2}}{G_{aa}}.
			\label{resolvent8}
		\end{equation}
\end{itemize}
\end{lemma}
The above result can be proved using Schur's complement formula, cf. \citet[Lemma 4.4]{Anisotropic}.
